Reconstructing Propositional Proofs in Type Theory

### 2017-10-24 paper/sections/introduction.tex
[ paper ] add the third paragraph in the introduction.

-----

% One approach to address the problem mentioned above
% consists of use a proof assistant as the proof checker.
% In this direction, we describe the usage of a proof assistant in type theory
% to reconstruct proofs delivered by \Metis prover.

@@

% Previous studies have reported proof-reconstruction for

>>>>

One approach to address the proof-reconstruction 
is integrating the \ATP, the \emph{source} system, with a proof assistant, the \emph{target} system.
The target system becomes in the proof checker.   
Previous studies have reported proof-reconstruction using proof assistant for classical logic where the development is at a mature stage.
In contrast, we choose a proof assistant for type theory
where proof verification becomes a type-checking task of the
proof-term following the Curry-Howard isomorphism.

@@

%
